Biotic invasions fuck with the manageability of pollination networks

### 2017-01-10 paper/draft_2.Rmd
Update glossary

Driver node
  ~ An unmatched node in a maximal cardinality matching or a maximum matching. From the control perspective driver nodes are those to which external control signals must ble applied in order to gain full control of the network.

Matched/unmatched link
  ~ A link if said to be *matched* if it is part of a matching and *unmatched* otherwise.

Matched/unmatched node
  ~ A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise.

Matching
  ~ A subset of links in which no two of them share a common starting or ending node.

Matching size
  ~ The number of matched links in a particular matching.

@@

Maximal cardinality matching
  ~ A matching with the largest possible size. In unweighted networks all maximal cardinality matchings are also maximum matchings.

Maximum matching
  ~ A matching with the largest possible size *and* weight.

Superior node
  ~ The node at the start of a matched link. From the control perspective superior nodes compose the chain that propagate the control signal(s) trough the network.

>>>>

Driver node
  ~ An unmatched node in a maximal cardinality matching or a maximum matching. From the control perspective, driver nodes are those to which external control signals must be applied in order to gain full control of the network.

Matched/unmatched link
  ~ A link is refered to as *matched* if it is part of a matching, and *unmatched* otherwise.

Matched/unmatched node
  ~ A node is refered to as *matched* if it is at the end of a matched link, and *unmatched* otherwise.

Matching
  ~ A set of links in which no two of them share a common starting or ending node.

Matching size
  ~ The number of matched links in a  matching.

@@

Maximal cardinality matching
  ~ A matching with the largest possible matching size. In unweighted networks, all maximal cardinality matchings are also maximum matchings.

Maximum matching
  ~ A matching with the largest possible matching size *and* matching weight.

Superior node
  ~ The node at the start of a matched link. From the control perspective, superior nodes make up the chain(s) that propagate the control signal(s) through the network.
